---
title: "RMD Presentation & Plotly <br>Diamonds Dataset"
author: "Ioan Catana"
date: "July 26, 2018"
output: ioslides_presentation
---

```{r knitr_setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

## Goal
In this document we will try to understand how different factors may influence the price of a diamond.
To answer that we use the `diamonds` dataset containing the prices and other attributes of almost 54,000 diamonds.
To make interpretation easier we choose a random sample of one thousand entries from the original dataset.

We plot weight of the diamond (`carat`) vs. price in US dollars (`price`) along the x/y axes. 
We also introduce another dimension to visualize the quality of the cut (`cut` having the following values: *Fair, Good, Very Good, Premium, Ideal*) as colors in the plot.

## Plotting the Data

```{r diamonds_plot}
library(plotly)
data(diamonds)
set.seed(112233)
small_diamonds <- diamonds[sample(nrow(diamonds), 1000), ]
plot_ly(small_diamonds, x = ~carat, y = ~price, color = ~cut,
        text = ~paste("Carat: ", carat, '<br>Price:', price, ' $','<br>Cut:', cut),
        type = "scatter", mode = "markers") %>%
  layout(title = "Diamonds Dataset")
```

